Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-11-29 paper/paper.tex

% declare the path(s) where your graphic files are
\graphicspath{{./pdf/}}

@@

\section{Architecture Overview}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

% declare the path(s) where your graphic files are
\graphicspath{{./diagrams/}}

@@

\section{Architecture Overview}
In this section we discuss the different architectures of the experimental
machines under test.  We will discuss CPU, GPU, and APU architectures in
terms of major differences that affect the performance of the device.

\subsection{CPU Architecture}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{GPU Architecture}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.
Blah blah blah see figure \ref{fig:cpu_arch}.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{cpu_architecture}
\caption{CPU Architecture}
\label{fig:cpu_arch}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{gpu_architecture}
\caption{GPU Architecture}
\label{fig:gpu_arch}
\end{figure}

\subsection{APU Architecture}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Related Work}
Ryoo et al. discuss optimization strategies for GPU versus CPU runtime
systems~\cite{Ryoo2007}.  However, their research is based on a GPU-only
or CPU-only implementation instead of a heterogeneous approach.  The work
presented in ~\cite{Jablin2011} describes a runtime and compiled framework
for improving memory access latency and reducing data transfer overhead
for GPU kernels.  Our work differs from this, because the kernel execution
was still being performed soley on the GPU, whereas our work investigates
kernel execution on multiple devices.

Computation via heterogeneous systems is a relatively new research area for
high performance computing.  The various frameworks and large number of
different accelerator devices can make this quite difficult for application
programmers to manage.  The StarPU system~\cite{Augonnet2009} presents a 
framework to allow for programmers to write numerical codelets and have them
automatically run on a heterogeneous system.  Scheduling work for this system
is one of the most difficult parts of the system, because of the various
overheads for work-sharing schemes. We simplify this work, by looking at a
two-device system, and focus on the performance characteristics of different
scheduling scheme.  Verner et al. use this approach to create a high-throughput
low-lantecy heterogeneous encryption system~\cite{Verner2011}.

Jimenez et al.~\cite{Jimenez2009} present a dynamic library which can be used
in a system to dynamically schedule tasks for GPU computation across various
processes. The method describes only looks at optimizing usage of the GPU across
the whole system, instead of optimizing a single application's performance.
